Discussion Draft

### 2020-03-17 doc/Discussion.rmd
small edits

## Greater within mouse variance in female

@@

#our results, female more (greater than tech error) male no significant difference

@@

##connection on evolution of transcriptional noise

@@

- Our results confirm previous findings of females having greater between cell variation (for indiviual females compared to males)
the results -- indicate there is more than can be due to technical noise (for oocytes vs spermatocytes spreads)
also all ovary collections were from early/ young mice -- not due to the maternal age effects, (which has to do with the stability of bivalents at metaphase -- after sexual maturity and ovulation (ref))

_sources of within animal variation_

 mouse and humans show greater between cell variance -- [@]

 this metric isn't really focused on (not many studies that examine inidivial level and both sexes)

3. Within mouse variance differences
In our results we observe more between cell variance in females (across all strains). This pattern has been observed in humans (Lynn et al).[@lynn2002]
(But results of reporting observations of single meiosis in both sexes).

(references, more within animal variance in
(number of crossovers per cell)
but maybe, rec landscapes in general)

>>>>

# Greater within mouse variance in female

@@

#our results, female more (greater than tech error) male no significant difference
#between cell variation

@@

## connection on evolution of transcriptional noise
# transcriptional noise and complex traits -- both show the same repsonses to different modes of selection

@@

**the within animal variation is equvillent to between cell variation**

Our results confirm previous findings from mice [@lynn2002] and humans of females having greater between cell variation compared to males.

While these (age, technical noise, ect) are potential sources of technical noise -- these results indecate this isn't due to technical noise or age effects.

Transcriptional noise and complex traits both show the same repsonses to different modes of selection, lower variation under stabilizing selection and greater variaion with relaxed selection. The difference in between
